Characterization of gaps in directly bonded Si compound optics

### 2014-04-16 AO_bondedSi.tex
overhaul Table 2

\section{Measurement strategy, conditions, and details}
The measurements were performed with an Agilent Cary 5000 UV-Vis-NIR spectrophotometer \cite{cary5000web}.  The typical measurement parameters and tool performance are listed below.  More details about the tool are available at the vendor's website.  Briefly, the tool has a double monochromator.  The double monochromator feature reduces scattered light.  The vendor reported linearity exceeds 40 dB.

@@

Table \ref{tab:tablenum3} shows some properties of the Cary5000.

%\caption{Summary of Cary 5000 Measurement parameters \label{tab:tablenum3}}
\begin{center}
    \begin{tabular}{l l}
        Parameter (Units) & Value \\ 
        Spectral sampling interval (nm) & 2.0 \\
        Spectral resolution (nm) & 5 \\
        Time per sample (s) & 0.1 \\
        Available measurement range (nm) & 175-3300 \\
        Typical measurement range (nm) & 1000-2500 \\
	Single mode RMS  (percent) & 0.02 \\
	Double mode RMS  (percent) & 0.002 \\
	Single mode mean drift (percent) & 0.20 \\
	Double mode mean drift (percent) & 0.02 \\
	Mean 0\% baseline correction (percent) & 0.03 \\
 	Beam size (mm x mm) & 2 x 8 \\
	Wavelengths of instrumental artifacts (nm) & stuff \\
        num1 & 1200 \\
        num2 & 1350 \\
        num3 & 1360-1450\\
        num4 & 1850 \\
        num5 & 1800-1950 \\
        num6 & 2000 \\
        Vendor-reported linearity range (dB) & 40 \\
        Directly measured linearity range (dB) & 24 \\
      \end{tabular}
\end{center}

>>>>

\section{Measurement strategy, conditions, and details}
We took transmission spectra of bonded Si wafers and pucks, and double side polished Si reference wafers. The spectrophotometer is a Agilent Cary 5000 UV-Vis-NIR.  The typical measurement parameters and tool performance are listed below.  More details about the tool are available at the vendor's website.  Briefly, the tool has a double monochromator.  The double monochromator feature reduces scattered light.  The vendor reported linearity exceeds 40 dB.

@@

\begin{table}[h!]
\caption{Summary of Cary 5000 Measurement parameters \label{tab:tablenum3}}
\begin{center}
\begin{tabular}{ c c }
\hline
        Parameter (Units) & Value \\ 
\hline
        Spectral sampling interval (nm) & 2.0 \\
        Spectral resolution (nm) & 5 \\
        Time per sample (s) & 0.1 \\
        Available measurement range (nm) & 175-3300 \\
        Typical measurement range (nm) & 1000-2500 \\
	Single mode RMS  (percent) & 0.02 \\
	Double mode RMS  (percent) & 0.002 \\
	Single mode mean drift (percent) & 0.20 \\
	Double mode mean drift (percent) & 0.02 \\
	Mean 0\% baseline correction (percent) & 0.03 \\
 	Beam size (mm x mm) & 2 x 8 \\
	Wavelengths of instrumental artifacts (nm) & stuff \\
        num1 & 1200 \\
        num2 & 1350 \\
        num3 & 1360-1450\\
        num4 & 1850 \\
        num5 & 1800-1950 \\
        num6 & 2000 \\
        Vendor-reported linearity range (dB) & 40 \\
        Directly measured linearity range (dB) & 24 \\
    \hline
    \end{tabular}
\end{center}
\end{table}
